Academic Advancement Advice: Author Articles as A.~A.

### 2018-03-14 citations/paper.tex
grep thing, restrict to english titles

Finally, I could run the author and citation tallier on all of the
JSON files. However, two of the files appeared to be empty. Although
this was only a small percentage of the articles, I did not want to
skip any because it's possible that they are arranged in a non-random
order (e.g. alphabetically!) and that this would bias the results. I
learned that although the AMiner database is helpfully split into
files each containing one million articles, for ease of handling, two
of these files are nonetheless slightly larger than $2^{31}$ bytes. Such
files cannot be cleanly sized with \verb+fstat+ (the \verb+st_size+
field has type \verb+off_t+, a signed 32-bit type in POSIX) and even
if you follow the standard advice of just treating it as unsigned
anyway, \verb+fread+ will simply fail when asked to read such a large
chunk\footnote{
%
  Curious why I am even using {\tt fstat} and {\tt fread}? I have my
  own library routine for reading a file into a string. When working
  with large files it's useful to avoid copying, because the contents
  of the file may be a significant fraction of all RAM---copying is
  not only expensive, but might temporarily exceed the available RAM.
  So, you need to allocate the buffer ahead of time and avoid resizing
  it (which often also performs a copy). It seems like something that
  everyone would want to do, but it's ridiculously hard to do portably
  in C or C++. Specifically, there seems to be no way to actually know
  the size of a file so that you can size the buffer ahead of time.
  For example, {\tt fseek} to {\tt SEEK\_END} and {\tt ftell} does
  {\em not} work (it has {\em undefined behavior}). The {\tt st\_size}
  field from {\tt stat} also does not give correct results e.g. when
  reading from the {\tt /proc} filesystem. My routine attempts to
  guess the size of the file and perform a single read in the case
  that the guess, while still usually avoiding copying or needless
  work in the case that it's an under- or over-estimate.
%
} despite the fact that it takes \verb+size_t+, an unsigned type. (?!)
So, another afternoon spent doing Computer Science. But all you need
to do of course is perform multiple sequential reads.

@@

Authors names appear in both ``Firstname Lastname'' order and
``Lastname Firstname'' (when this grammar is even applicable).
Therefore, I considered alphabetizing from front to back (by
space-separated token) as well as back to front. This produces two
different graphs. I also rejected a large number entries when I could
not place the name in alphabetical order because its first character
was not ASCII. Later non-ASCII charactes are OK, and are just sorted
by their UTF-8 encodings (or whatever garbage is in the file). This of
course produces a bias (excluding authors who write their names in
e.g. Cyrillic and CJK scripts), although it's not clear how to assess
the alphabetical hypothesis for them.

@@

multiple hypothesized causes:

- When doing a last-minute

- Some academics try to \verb+fread+ all papers into memory, but
  it fails on the file that's just slightly larger than $2^{31}$ bytes,
  and so the papers therein don't get cited, and those papers are
  alphabetically in the middle or end of the alphabet.

>>>>

Finally, I could run the author and citation tallier on all of the
JSON files. However, two of the files appeared to be empty. Although
this was only a small percentage of the articles, I did not want to
skip any because it's possible that they are arranged in a non-random
order (e.g. alphabetically!) and that this would bias the results. I
learned that although the AMiner database is helpfully split into
files each containing one million articles, for ease of handling, two
of these files are nonetheless slightly larger than $2^{31}$ bytes. Such
files cannot be cleanly sized with \verb+fstat+ (the \verb+st_size+
field has type \verb+off_t+, a signed 32-bit type in POSIX) and even
if you follow the standard advice of just treating it as unsigned
anyway, \verb+fread+ will simply fail when asked to read such a large
chunk\footnote{
%
  Curious why I am even using {\tt fstat} and {\tt fread}? I have my
  own library routine for reading a file into a string. When working
  with large files it's useful to avoid copying, because the contents
  of the file may be a significant fraction of all RAM---copying is
  not only expensive, but might temporarily exceed the available RAM.
  So, you need to allocate the buffer ahead of time and avoid resizing
  it (which often also performs a copy). It seems like something that
  everyone would want to do, but it's ridiculously hard to do portably
  in C or C++. Specifically, there seems to be no way to actually know
  the size of a file so that you can size the buffer ahead of time.
  For example, {\tt fseek} to {\tt SEEK\_END} and {\tt ftell} does
  {\em not} work (it has {\em undefined behavior}). The {\tt st\_size}
  field from {\tt stat} also does not give correct results e.g. when
  reading from the {\tt /proc} filesystem. My routine attempts to
  guess the size of the file and perform a single read in the case
  that the guess is correct, while still usually avoiding copying or
  needless work in the case that it's an under- or over-estimate.
%
} despite the fact that it takes \verb+size_t+, an unsigned type. (?!)
So, another afternoon spent doing Computer Science. But all you need
to do of course is perform multiple sequential reads.

@@

Author names appear in both ``Firstname Lastname'' order and
``Lastname Firstname'' (when this grammar is even applicable).
Therefore, I analyzed alphabetizing from front to back (by
space-separated token) as well as back to front. I also rejected a
large number entries when I could not place the name in alphabetical
order because its first character was not ASCII. Later non-ASCII
characters are OK, and are just sorted by their UTF-8 encodings (or
whatever garbage is in the file). This of course produces a bias
(excluding authors who write their names in e.g. Cyrillic and CJK
scripts), although it's not clear how to assess the alphabetical
hypothesis for them.

@@

These CDFs show that---as expected!---there is a bias towards citing
authors alphabetically early, whether we order alphabetically by
``first name'' or ``last name.''

There are multiple hypothesized causes:
\begin{itemize}

\item When writing a last-minute ``related work'' section, authors
  sometimes find papers to cite in alphabetical order, for example, by
  reading another paper's bibliography, which is sometimes
  alphabetized.

\item Some academics try to \verb+fread+ all papers into memory, but
  it fails on the file that's just slightly larger than $2^{31}$ bytes,
  and so the papers therein don't get cited, and those papers are
  alphabetically in the middle or end of the alphabet.

\item When applying for grad school, tenure track faculty jobs, grants,
  and so on, packets are alphabetized ``for fairness,'' and the
  disposition of the committee becomes more irritable as they make
  progress through the set.

\item Decreased access to pie and  unfair situations in
  youth cause a lifelong predisposition to failure.

\end{itemize}

% 313779.  書評	29582	1	0.000068
% 313778.  インタビュー	20547	1	0.000097
% 313777.  facharzt	85315	9	0.000117
% 313776.  f3d	125257	15	0.000128
% 313775.  recenzja	63568	8	0.000142
% 313774.  newhaven	13296	1	0.000150
% 313773.  secrétaire	12267	1	0.000163
% 313772.  zahnarzt	17958	2	0.000167
% 313771.  libguides	389727	72	0.000187
% 313770.  硏究	12961	2	0.000231
% 313769.  그	15984	3	0.000250
% 313768.  kitas	7713	1	0.000259
% 313767.  シンポジウム	18539	4	0.000270
% 313766.  特集	878011	240	0.000274
%

\begin{figure}
  \begin{center}
  \includegraphics[width=0.475 \textwidth]{wordstats}
  \end{center}
  \caption{ CDF for words arranged alphabetically. This is just as
    in Figure~\ref{fig:authorcdf}, but since each entry is a single
    word, there is no need to treat forward and backward differently.
    Again, we see a small alphabetical bias, with citations leading
    articles for most of the range. In fact, papers that include the
    very first word, ``a'', are cited $1.3\times$ as often as the
    average paper. Other common and advantageous words are visible
    as clear bumps. (See Section XXX)
  } \label{fig:wordcdf}
\end{figure}

% Tourney -- what is wrong here?
%  1000.000 Mrounds:
%  (69.66 vs. 72.69 Gcit) (6.72 vs. 7.20 Gart) (0.281 vs. 0.295 Gwin)
%  (0.958361 L:R cit) (0.933736 L:R art) (0.280867 vs. 0.295327 win rate)
